Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-12 manuscripts/manuscript.Rmd
additional runs at different NPV reduction calibration points

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients
that induce the same reduction in maximum expected NPV. For example,
the dashed vertical line in Figure 2 maps the needed cost coefficient
$c_i$, for each penalty function, such that the fishery is worth `r 100*(1-reduction)`%
of its unconstrained value when optimally managed.

@@

These patterns are consistent across stochastic replicates over a
range of penalty magnitudes. The comparisons shown in Figure 3 are
for one realization (i.e. a particular sequence of random number draws
representing environmental variability) and are made for one particular
magnitude of policy adjustment costs, which have been calibrated to equal
to `r reduction *100`% of $NPV_0({\bf h_0^*})$.  To demonstrate this,
we solved for the optimal policy under each of the three adjustment
cost scenarios for `r length(c2)` different $c_i$ coefficients. For each
resulting policy, we then simulated 50 stochastic replicates of the stock
dynamics managed under that policy.  To summarize the patterns shown
in Figure 3 and characterize the impact of increasingly large fraction
of the economic value (NPV) being consumed by policy adjustment costs,
we examine the response of several summary statistics to increasing
adjustment penalties (as a fraction of the adjustment-free value) in
Figure 4.  We show the impact of policy adjustment costs on the variance &
autocorrelation of the harvests through time.

@@

@@

To do so, we will simulate managing a fish stock when adjustments are costly.
We will perform 100 replicate simulations of this for each of the three
cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will
use two different management policies: one which ignores the adjustment costs,
(that is, the Reed optimum policy, $\Pi_0$), and a second which accounts for the
adjustment cost in place.

>>>>

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients
that induce the same reduction in maximum expected NPV. For example,
the dashed vertical line in Figure 2 maps the needed cost coefficient
$c_i$, for each penalty function, such that the fishery is worth `r 100*(1-reduction)`%
of its unconstrained value when optimally managed. To demonstrate that the results
shown here are independent of this choice of calibrating to a `r 100*(1-reduction)`%
reduction, we conduct the same analysis with a 10% and 30% reduction rate as well.
The corresponding figures can be found in the Supplemental Materials.

@@

These patterns are consistent across stochastic replicates over a
range of penalty magnitudes. The comparisons shown in Figure 3 are
for one realization (i.e. a particular sequence of random number draws
representing environmental variability) and are made for one particular
magnitude of policy adjustment costs, which have been calibrated to equal
to `r reduction *100`% of $NPV_0({\bf h_0^*})$.  To demonstrate this,
we solved for the optimal policy under each of the three adjustment
cost scenarios for `r length(c2)` different $c_i$ coefficients. For each
resulting policy, we then simulated `r length(reps)` stochastic replicates of the stock
dynamics managed under that policy.  To summarize the patterns shown
in Figure 3 and characterize the impact of increasingly large fraction
of the economic value (NPV) being consumed by policy adjustment costs,
we examine the response of several summary statistics to increasing
adjustment penalties (as a fraction of the adjustment-free value) in
Figure 4.  We show the impact of policy adjustment costs on the variance &
autocorrelation of the harvests through time.

@@

In the supplemental material, Figures S9-S12 illustrate that the 
these qualitative patterns still hold at when the models are calibrated 
to a reduction in NPV of 10% or 30%, though naturally the magnitude
of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).

@@

To do so, we will simulate managing a fish stock when adjustments are costly.
We will perform `r length(reps)` replicate simulations of this for each of the three
cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will
use two different management policies: one which ignores the adjustment costs,
(that is, the Reed optimum policy, $\Pi_0$), and a second which accounts for the
adjustment cost in place.

### 2015-05-12 manuscripts/supplement.Rmd
additional runs at different NPV reduction calibration points

\appendix
\renewcommand{\thefigure}{S\arabic{figure}}

@@

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

@@

@@

@@

@@

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}
\appendix

@@

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn) 
dt_s$penalty_fn <- factor(dt3$penalty_fn, levels=c("L1", "L2", "fixed"))

@@

s2df$penalty_fn <- factor(f4df$penalty_fn, levels = c("L1", "L2", "fixed"))

@@

dt$penalty_fn <- factor(dt$penalty_fn, levels = c("L1", "L2", "fixed"))

@@

table1_long$penalty.fn <- factor(table1_long$penalty.fn, levels = c("L1", "L2", "fixed"))

@@

## Robustness to reduction level

```{r}
source("components/vary_reduction.R")
```

Figures S9-S12 illustrate that the 
these qualitative patterns still hold at when the models are calibrated 
to a reduction in NPV of 10% or 30%, though naturally the magnitude
of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).

```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.  This results in a less pronounced version of the same qualitative pattern."}
p3 <- ggplot(low$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 10% reduction in NPV")

p3
```

```{r Figure_S10, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.  This results in a more pronounced version of the same qualitative pattern."}
p3 <- ggplot(high$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 30% reduction in NPV")
p3
```

```{r Figure_S11, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 10% reduction in NPV rather than 25%.  The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
p4 <- ggplot(low$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
  coord_cartesian(xlim = c(0, .3)) + 
  scale_color_discrete(labels=relabel, name="cost model") + 
  scale_fill_discrete(labels=relabel, name="cost model")

p4a <- p4 + 
  stat_summary(aes(y=autocorrelation),
               fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
  xlab("") + 
  labs(title="Summary statistics under a 10% reduction in NPV")

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")

grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,2))
```

```{r Figure_S12, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 30% reduction in NPV rather than 25%.  The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
p4 <- ggplot(high$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
  coord_cartesian(xlim = c(0, .3)) + 
  scale_color_discrete(labels=relabel, name="cost model") + 
  scale_fill_discrete(labels=relabel, name="cost model")

p4a <- p4 + 
  stat_summary(aes(y=autocorrelation),
               fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
  xlab("") + 
  labs(title="Summary statistics under a 30% reduction in NPV")

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")

grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,2))
```
